
```{r}

# tensorflow::install_tensorflow(extra_packages='pillow',version = "2.4.0")



library(unet)
library(tensorflow)
library(keras)
library(tfdatasets)
library(tidyverse)
library(rsample)
library(reticulate)
library(magick)
library(imager)

TRAIN<- file.path("c:/kaggletemp/HuBMAP/train_images/")
MASK<- file.path("c:/kaggletemp/HuBMAP/mask_images/")
TEST<- file.path("c:/kaggletemp/HuBMAP/test/")
BASE<-file.path("c:/kaggletemp/HuBMAP/")
BASET<-file.path("c:/kaggletemp/HuBMAP/train/")
EVAL<-file.path("c:/kaggletemp/HuBMAP/evaluation/")

gpu_devices =  tf$config$experimental$list_physical_devices("GPU")[[1]]
tf$config$experimental$set_memory_growth(gpu_devices, T)

#model<-load_model_hdf5(file.path(BASE,"models"), custom_objects = c("bce_dice_loss"= bce_dice_loss, "dice"=dice))

```
```{r}
bce_dice_loss <- function(y_true, y_pred) {
    result <- loss_binary_crossentropy(y_true, y_pred) +
        (1 - dice(y_true, y_pred))
    return(result)
} 

dice <- custom_metric("dice", function(y_true, y_pred, smooth = 0) {
  y_true_f <- k_flatten(y_true)
  y_pred_f <- k_flatten(y_pred)
  intersection <- k_sum(y_true_f * y_pred_f)
  (2 * intersection + smooth) / (k_sum(y_true_f) + k_sum(y_pred_f) + smooth)
})
#model<-load_model_hdf5(file.path(BASE,"models","m8774.hdf5"), custom_objects = c("bce_dice_loss"= bce_dice_loss, "dice"=dice))
#model<-load_model_hdf5(file.path(EVAL,"m500_50_12000.hdf5"), custom_objects = c("bce_dice_loss"= bce_dice_loss, "dice"=dice))

BATCH_SIZE =4
SIZE = 2^7

```

lets filter the images < 300k (they are all artefacts)

```{r}
# ###################################################################################################
# #train
# 
# xt <- list.files(TRAIN,full.names = TRUE)
# xt<- xt[sapply(xt, file.size) > 300000]
# extt<- xt %>% map( . %>% gsub(pattern = file.path(TRAIN,"image"), replacement = ""))
# msk<-   paste0(file.path(MASK,"mask"),extt) %>% unlist
# imagest <- tibble(
#   img = xt,
#   mask =msk
#   ) %>%
#   sample_n(3) %>%
#   map(. %>% magick::image_read() %>% magick::image_resize("128x128"))
# 
# out <- magick::image_append(c(
#   magick::image_append(imagest$img, stack = TRUE),
#   magick::image_append(imagest$mask, stack = TRUE)
#   )
# )
# plot(out)
# ##################################################################################################
# #mask
# xm <- list.files(MASK,full.names = TRUE)
# xm<- xm[sapply(xm, file.size) > 1000]
# exmt<- xm %>% map( . %>% gsub(pattern = file.path(MASK,"mask"), replacement = ""))
# ttrain<-   paste0(file.path(TRAIN,"image"),exmt) %>% unlist
# imagesm <- tibble(
#   image = ttrain,
#   mask = xm
#   ) %>%
#   sample_n(3) %>%
#   map(. %>% magick::image_read() %>% magick::image_resize("128x128"))
# 
# 
# out <- magick::image_append(c(
#   magick::image_append(imagesm$mask, stack = TRUE),
#   magick::image_append(imagesm$image, stack = TRUE)
#   #magick::image_append(images$predicted_mask, stack = TRUE)
#   )
# )
# plot(out)


```




```{r}

# takes additional parameters, including number of downsizing blocks, 
# number of filters to start with, and number of classes to identify
# see ?unet for more info

# BATCH_SIZE =28
# SIZE = 2^7


xt <- list.files(TRAIN,full.names = TRUE)
xt<- xt[sapply(xt, file.size) > 50 *1000]
extt<- xt %>% map( . %>% gsub(pattern = file.path(TRAIN,"image"), replacement = ""))
msk<-   paste0(file.path(MASK,"mask"),extt) %>% unlist
imagest <- tibble(
  img = xt,
  mask =msk
  ) 

xm <- list.files(MASK,full.names = TRUE)
xm<- xm[sapply(xm, file.size) >500]
exmt<- xm %>% map( . %>% gsub(pattern = file.path(MASK,"mask"), replacement = ""))
ttrain<-   paste0(file.path(TRAIN,"image"),exmt) %>% unlist
imagesm <- tibble(
  img = ttrain,
  mask = xm
  ) 
######################################################## debug

# imagesm <- tibble(
#   img = ttrain,
#   mask = xm
#   ) %>%
#   sample_n(3) %>%
#    map_depth(2,. %>% load.image )
# fcc<-function(img,pred){
#   out<-colorise(img,pred %>% as.pixset,"blue",alpha = .3)
#   out
# }
# out<- map2(imagesm$img,imagesm$mask, fcc) %>% imappend(axis="x")
# plot(out)
####################################################
set.seed(123)

imagest$glo <- imagest$mask %in% xm
csplit<- initial_split(imagest, prop = 9/10,strata = glo)
train.data<- training(csplit) %>% select(-glo)
test.data<- testing(csplit) %>% select(-glo)


# #true
# nm<-sample(nrow(imagesm), 500)
# 
# #the true left
# tl<- imagesm[-nm,]
# #test, no true
# noglo<-!imagest$img %in% imagesm$img
# noglot<-imagest[noglo,]
# 
# 
# nt<- sample(nrow(noglot),9000)
# ntest<- sample(nrow(noglot),50)
# train.data<- rbind(imagesm[-nm,],noglot[nt,]) %>% sample_n(nrow(.))
# test.data<-rbind(imagesm[nm,], noglot[ntest,] )%>% sample_n(nrow(.))


random_bsh <- function(img) {
  img %>%
    tf$image$random_brightness(max_delta = 0.3) %>%
    tf$image$random_contrast(lower = 0.5, upper = 0.7) %>%
    tf$image$random_saturation(lower = 0.5, upper = 0.7) %>%
    # make sure we still are between 0 and 1
    tf$clip_by_value(0, 1)
}

# training_dataset <- training_dataset %>%
#   dataset_map(~.x %>% list_modify(
#     img = random_bsh(.x$img)
#   ))
# 


# 
# example <- training_dataset %>% as_iterator() %>% iter_next()
# example$img %>% as.array() %>% image_read() %>% plot()
# 

create_dataset <- function(data, train, batch_size = BATCH_SIZE) {
  
  dataset <- data %>% 
    tensor_slices_dataset() %>% 
   dataset_map(~.x %>% list_modify(
    # decode_jpeg yields a 3d tensor of shape (1280, 1918, 3)
    img = tf$image$decode_png(tf$io$read_file(.x$img)),
    # decode_gif yields a 4d tensor of shape (1, 1280, 1918, 3),
    # so we remove the unneeded batch dimension and all but one 
    # of the 3 (identical) channels
    mask =tf$image$decode_png(tf$io$read_file(.x$mask))
  ))%>% 
  dataset_map(~.x %>% list_modify(
    img = tf$image$convert_image_dtype(.x$img, dtype = tf$float32),
    mask = tf$image$convert_image_dtype(.x$mask, dtype = tf$float32)
  )) %>%
   dataset_map(~.x %>% list_modify(
      img = tf$image$resize(.x$img, size = shape(SIZE, SIZE)),
      mask = tf$image$resize(.x$mask, size = shape(SIZE, SIZE))[,,1,drop=F]
    )) #%>%
  # dataset_map(~.x %>% list_modify(
  #     img = k_expand_dims(.x$img, axis = 1),
  #     mask = k_expand_dims(.x$mask, axis = 1)
  #   ))
  
x<- dataset %>% as_iterator()%>% iter_next()

#  data augmentation performed on training set only
  # if (train) {
  #   dataset <- dataset %>%
  #     dataset_map(~.x %>% list_modify(
  #       img = random_bsh(.x$img)
  #     ))
  # }

  # shuffling on training set only
  if (train) {
    dataset <- dataset %>% 
      dataset_shuffle(buffer_size = batch_size*2^4)
  }
  
  # train in batches; batch size might need to be adapted depending on
  # available memory
  dataset <- dataset %>% 
    dataset_batch(batch_size)
  
  dataset %>% 
    # output needs to be unnamed
    dataset_map(unname) 
}

training_dataset <- create_dataset(train.data, train = TRUE)
validation_dataset <- create_dataset(test.data, train = FALSE)

#model <- unet(input_shape = c(SIZE, SIZE, 3))
##########################################################################################
x<- training_dataset %>% as_iterator() %>% iter_next() %>% .[[1]] %>% .[1,,,] %>% k_expand_dims(axis=1)
hub_layer(x)
library(tfhub)
ai<- "https://tfhub.dev/nvidia/unet/industrial/class_9/1"

input <- layer_input(shape = c(SIZE, SIZE, 3))
hub_layer <- layer_hub(handle = ai, trainable=TRUE)


output <- input %>%
    layer_lambda(function(x) tensorflow::tf$image$resize(x, c(224L, 224L))) %>% 
    hub_layer %>%
    #layer_global_max_pooling_2d() %>% 
     layer_dense(units = 1,activation = "sigmoid")

model <- keras_model(input, output)

# base_model<- model <- application_densenet(weights = NULL,
#                                            input_shape = c(SIZE, SIZE, 3),
#                                            include_top = F,
#                                            classes = 1)
# predictions<-base_model$output %>%
#   layer_dense(units = 1,activation = "sigmoid")
# model <- keras_model(inputs = base_model$input, outputs = predictions)

##########################################################################################
summary(model)


model %>% compile(
  optimizer =optimizer_rmsprop(lr=1e-4),# optimizer_nadam(lr = 1e-4),
  loss = bce_dice_loss,
  metrics = list(dice,metric_binary_accuracy)
)


hist<- model %>% 
  fit(
  training_dataset,
  epochs = 25,
  #batch_size=2^10,
  verbose = 1,
  #validation_split = 0.2
  validation_data = validation_dataset
    )


 save_model_hdf5(model, "m8774.hdf5")
  save_model_hdf5(model,file.path(EVAL, "m500_50_12000.hdf5") )

# 2021-01-17 04:36:35.548427: I tensorflow/core/kernels/data/shuffle_dataset_op.cc:230] Shuffle buffer filled.
# Epoch 23/25
# 244/244 [==============================] - 92s 331ms/step - loss: 0.1490 - dice: 0.8922 - binary_accuracy: 0.9899 - val_loss: 0.3991 - val_dice: 0.8688 - val_binary_accuracy: 0.9490
# 2021-01-17 04:38:06.351462: I tensorflow/core/kernels/data/shuffle_dataset_op.cc:177] Filling up shuffle buffer (this may take a while): 1823 of 2048
# 2021-01-17 04:38:07.607702: I tensorflow/core/kernels/data/shuffle_dataset_op.cc:230] Shuffle buffer filled.
# Epoch 24/25
# 244/244 [==============================] - 86s 308ms/step - loss: 0.1396 - dice: 0.8986 - binary_accuracy: 0.9904 - val_loss: 0.3858 - val_dice: 0.8758 - val_binary_accuracy: 0.9519
# 2021-01-17 04:39:32.863342: I tensorflow/core/kernels/data/shuffle_dataset_op.cc:177] Filling up shuffle buffer (this may take a while): 1837 of 2048
# 2021-01-17 04:39:34.006519: I tensorflow/core/kernels/data/shuffle_dataset_op.cc:230] Shuffle buffer filled.
# Epoch 25/25
# 244/244 [==============================] - 92s 333ms/step - loss: 0.1402 - dice: 0.8986 - binary_accuracy: 0.9906 - val_loss: 0.3310 - val_dice: 0.8774 - val_binary_accuracy: 0.9527
```









```{r}



# 
# 
# batch <- validation_dataset %>% as_iterator() %>% iter_next()
# predictions <- predict(model, batch[[1]])
# 
# images <- tibble(
#   image = batch[[1]] %>% array_branch(1),
#   predicted_mask = predictions[,,,1] %>% array_branch(1),
#   mask = batch[[2]][,,,1]  %>% array_branch(1)
# ) %>%
#   sample_n(2) %>%
#   map_depth(2, function(x) {
#     as.raster(x) %>% magick::image_read()
#   }) %>%
#   map(~do.call(c, .x))
# 
# 
# out <- magick::image_append(c(
#   magick::image_append(images$mask, stack = TRUE),
#   magick::image_append(images$image, stack = TRUE),
#   magick::image_append(images$predicted_mask, stack = TRUE)
#   )
# )
# 
# plot(out)


```

```{r}
library(imager)
thr=.1

batch <- validation_dataset %>% as_iterator() %>% iter_next()
predictions <- predict(model, batch[[1]])

images <- tibble(
  image = batch[[1]] %>% array_branch(1),
  predicted_mask = predictions[,,,1] %>% array_branch(1),
  mask = batch[[2]][,,,1]  %>% array_branch(1)
) %>% 
  sample_n(4) %>%
  map_depth(2, as.cimg)

images$predicted_mask<- images$predicted_mask %>% map( function(x) x > thr)
images$mask<- images$mask %>% map( function(x) x > thr)

fcc<-function(img,pred){
  out<-colorise(img,pred,"blue",alpha = .3)
  out
}
out.pred<- map2(images$image,images$predicted_mask, fcc) %>% imappend(axis="x")
out.true<- map2(images$image, images$mask, fcc) %>% imappend(axis="x")
out<-imappend(list(out.pred,out.true),axis = "y")
plot(out, main= "pred (first) x true")

# out <- magick::image_append(c(
#   magick::image_append(images$mask, stack = TRUE),
#   magick::image_append(images$image, stack = TRUE), 
#   magick::image_append(images$predicted_mask, stack = TRUE)
#   )
# )
# 
# plot(out)


```




```{r}
# library(imager)
# x <- list.files(MASK,full.names = TRUE)
# x<- x[sapply(x, file.size) > 1700]
# ext<- x %>% map( . %>% gsub(pattern = file.path(MASK,"mask"), replacement = ""))
# 
# ttrain<-   paste0(file.path(TRAIN,"image"),ext) %>% unlist
# ims <- tibble(
#   img = ttrain,
#   mask = x
#   )
# 
# x<-ims[1:3,]
# xd<- create_dataset(x,train=F)
# predictions<- predict(model, xd) 
# 
# 
# xm <-x$mask %>% map(. %>% load.image) %>% 
#   map(. %>%  imsplit("c") %>% .[[1]]) %>%
#   map(. %>% imresize(1/1)) %>% 
#   map(. %>% .[,,,1] ) %>%
#   map(. %>% image_to_array)
# xim<-x$img %>% map(. %>% load.image) %>% 
#   map(. %>% imresize(1/1)) %>%
#    map(. %>% .[,,1,] %>% image_to_array)
# images <- tibble(
#   image = xim,
#   predicted_mask = predictions %>% array_branch(1),
#   mask = xm
# ) %>% 
#   map_depth(2, function(x) {
#     as.cimg(x) %>% magick::image_read()
#   }) %>% 
#   map(~do.call(c, .x))
# out <- magick::image_append(c(
#   magick::image_append(images$mask, stack = TRUE),
#   magick::image_append(images$image, stack = TRUE), 
#   magick::image_append(images$predicted_mask, stack = TRUE)
#   )
# )
# 
# plot(out)


```

## Submition 
```{r}
k=3
ftiff<- list.files(TEST, pattern = "*.tiff")
impath<-ftiff[3]
basedir<- file.path("C:/kaggletemp/HuBMAP/")
dataset<- read_csv(file.path(basedir,"HuBMAP-20-dataset_information.csv"))

im<-image_read(file.path(TEST,impath))
makeimg<-function(i,j,im=im){
  dest<- paste0(512,"x",512, "+",i, "+", j)
  imx<- image_crop(im,dest) %>% .[[1]] %>% as.numeric %>% #array(dim=c (1,SIZE,SIZE,3)) %>%
  tf$image$convert_image_dtype( dtype = tf$float32)  %>%
  tf$image$resize( size = shape(SIZE,SIZE)) %>% k_expand_dims(axis=1)
}
      
  shape<-dataset %>% subset(image_file == ftiff[k] ) %>% dplyr::select(width_pixels, height_pixels) %>% unlist %>% as.vector
  nl<-c( seq(0,shape[1]-512, 512), shape[1]-512)
  nc<-c( seq(0,shape[2]-512, 512) , shape[2]-512)
  nn<-expand.grid(nl,nc)
  # walk2(nn[,1],nn[,2],makePng,im=im,mask=mask)
  
predsub<-array(0,dim=c(shape[1],shape[2]))
for(i in seq_len(nrow(nn)) ){
  img<- makeimg(nn[i,1],nn[i,2],im=im) 
  pred<- predict(model, img) %>%  tf$image$resize( size = shape(512,512)) %>% 
    k_squeeze(axis=1) %>% k_squeeze(axis=3) %>% as.array(dim=c(512,512))
  if( img %>% as.array %>% mean==0){next}else{
  #pred[pred > thr]<- 1, pred[pred< thr]<-0
  pred<- pred > thr
  }
  predsub[  (nn[i,1]+1):(nn[i,1]+512),  (nn[i,2]+1):(nn[i,2]+512)] <- pred
}
x<- imsub %>% as.cimg


#   
# outx <-array(0,dim=c(shape[1],shape[2],1,3)) 
# for(i in seq_len(nrow(nn)) ){
#   img<- makeimg(nn[i,1],nn[i,2],im=im) 
#   pred<- predict(model, img) %>%  tf$image$resize( size = shape(512,512)) %>% 
#     k_squeeze(axis=1) %>% k_squeeze(axis=3) %>% as.array(dim=c(512,512)) %>% as.cimg
#   
#   img<- img %>%  tf$image$resize( size = shape(512,512)) %>%
#     k_squeeze(axis=1) %>% k_expand_dims(axis=3) %>% as.array %>% as.cimg
#   
#    if( img %>% as.array %>% mean==0){pred<- pred > 1}else{
#   #pred[pred > thr]<- 1, pred[pred< thr]<-0
#   pred<- pred > thr
#   }
#   x<-colorise(img,pred,"blue",alpha = .3)
#   
#   outx[  (nn[i,1]+1):(nn[i,1]+512),  (nn[i,2]+1):(nn[i,2]+512),1,3] <- x %>% as.array()
# }
# 
# 
# 
# 
# 
# 
# colorise(a[[1]],b[[1]],"blue",alpha = .3)




```


```{r}
mask2rle <- function(mm) {
   idx<- which(mm==1)
  if (length(idx) == 0) return("")
  
  # Make sure  values are sorted
  idx <- sort(idx)
  
  # Array of starting positions and run lengths
  starts <- c()
  runs <- c()
  
  # Loop
  starts <- c(starts, idx[1])
  run <- 1
  for (i in 2:length(idx)) { #run
    if (idx[i-1] + 1 == idx[i]) {
      run <- run + 1
    } else { #stop
      runs <- c(runs, run)
      starts <- c(starts, idx[i])
      run <- 1
    }
  }
  
  # Last run length needs special handling
  runs <- c(runs, run)
  
  # Sanity check
  stopifnot(length(starts) == length(runs))
  
  # zip starts and runs as space delimited list
  return(paste0(mapply(list, paste(starts, runs)), collapse = " "))
  
}
idx2rle <- function(idx) {
  if (length(idx) == 0) return("")
  
  # Make sure  values are sorted
  idx <- sort(idx)
  
  # Array of starting positions and run lengths
  starts <- c()
  runs <- c()
  
  # Loop
  starts <- c(starts, idx[1])
  run <- 1
  for (i in 2:length(idx)) { #run
    if (idx[i-1] + 1 == idx[i]) {
      run <- run + 1
    } else { #stop
      runs <- c(runs, run)
      starts <- c(starts, idx[i])
      run <- 1
    }
  }
  
  # Last run length needs special handling
  runs <- c(runs, run)
  
  # Sanity check
  stopifnot(length(starts) == length(runs))
  
  # zip starts and runs as space delimited list
  return(paste0(mapply(list, paste(starts, runs)), collapse = " "))
  
}
# print(mask2rle(c(1,2,3,10,11,12,13,14)))


# rleR <- function(x){
#  # x = sort(x) # Sort x first
#   y = diff(x) # Find successive differences - most should be 1's
#   runs = base::rle(y) # Use the rle function in base R to compute the runs - we want to find sequences of 1's
#   z = (runs$lengths)[which(runs$values==1)] + 1 # Get the run length
#   indices = c(1, x[which(diff(x) != 1) + 1]) # Get the starting positions
#   return (paste(c(rbind(indices, z)), collapse = " ")) # Put in the required format
# }

# Examples
# rleR(c(1:5, 10:15))
# rleR(c(1,2,3,10,11,12,13,14))


# idx<- which(predsub==1)
# z<-rlex(idx) #works

```

#Lets make a toy example
```{r}
# mask2rle <- function(x){
#   #x = which(x==1) # Sort x first
#   y = diff(x) # Find successive differences - most should be 1's
#   runs = base::rle(y) # Use the rle function in base R to compute the runs - we want to find sequences of 1's
#   z = (runs$lengths)[which(runs$values==1)] + 1 # Get the run length
#   indices = c(1, x[which(diff(x) != 1) + 1]) # Get the starting positions
#   return (paste(c(rbind(indices, z)), collapse = " ")) # Put in the required format
# }

# Examples

# mask2rle<- function(x){
#    pixel <- x %>% as.vector
#    xx<- rle(pixel)
#    ids<- which (xx$values != 0 )
#    lls<- xx$lengths[ids]
#    cs<- cumsum(xx$lengths)
#    css<-cs[ids-1]+1
#    return( paste(css,lls,sep = " ", collapse = " ") )
# }
# mask2rle<- function(pixel){
#   pixel<- which(pixel == 1)
#    xx<- rle(pixel)
#    ids<- which (xx$values != 0 )
#    lls<- xx$lengths[ids]
#    cs<- cumsum(xx$lengths)
#    css<-cs[ids-1]+1
#    return( paste(css,lls,sep = " ", collapse = " ") )
# }



# rle2mask <- function(mask_rle,shape){
#   sl<- mask_rle   %>% strsplit(" ") %>% .[[1]] %>% as.numeric
#   starts<-sl[seq(1,(length(sl) -1),2)]
#   lengths<-sl[seq(2,length(sl),2)]
#   ends<-starts + lengths -1
#   img<- matrix(0,shape[1] * shape[2]  )
#   ids<-lapply(1:length(starts),function(i){seq(starts[i],ends[i],1)}) %>% unlist
#   img[ids,1]<-1
#   #img<-rep(img,3)
#   dim(img)<-c(shape[1],shape[2],1)
#   return((img))
# }
rle2mask <- function(mask_rle,shape){
  sl<- mask_rle   %>% strsplit(" ") %>% .[[1]] %>% as.numeric
  starts<-sl[seq(1,(length(sl) -1),2)] 
  lengths<-sl[seq(2,length(sl),2)]
  ends<-starts + lengths -1
  img<- matrix(0,ncol= shape[1] ,nrow=shape[2]  )
  #img<-imfill(0,x=shape[2],y=shape[1],z=1)
  ids<-lapply(1:length(starts),function(i){seq(starts[i],ends[i],1)}) %>% unlist
  img[ids]<-1
 # dim(img)<-c(shape[2],shape[1])
  img<-  img  #%>%imager::save.image("test.png")
    # dim(img)<-c(shape[2],shape[1],1)
    # img %>% image_read() %>% image_write("magictest.png", format = "png")
  return((img))
}
```

test_rotation

```{r}
thr = .6
train<- read_delim(file.path(BASE,"train.csv"), delim = ",")
test<-read_csv(file.path(BASE,"sample_submission.csv"))
dataset<- read_csv(file.path(BASE,"HuBMAP-20-dataset_information.csv"))
ffnames<-list.files(BASET, full.names = F,pattern = "*.tiff") %>% gsub(pattern = ".tiff",replacement =  "")

makeMask<-function(i){
  mask_rle<- train %>% subset(id == ffnames[i]) %>% dplyr::select(encoding) %>% pull
  shape_rle<-dataset %>% subset(image_file == paste0(ffnames[i], ".tiff")) %>% dplyr::select(width_pixels, height_pixels) %>% unlist %>% as.vector
  mask<- rle2mask(mask_rle, shape_rle)  %>% as.cimg
  return(mask)
}

k=2
impath<-file.path(BASET,paste0(ffnames[k],".tiff") )

im<-image_read(impath)
makeimg<-function(i,j,im=im){
  dest<- paste0(512,"x",512, "+",i, "+", j)
  imx<- image_crop(im,dest) %>% .[[1]] %>% as.numeric %>% aperm(perm = c(2,1,3))%>%#array(dim=c (1,SIZE,SIZE,3)) %>%
  tf$image$convert_image_dtype( dtype = tf$float32)  %>%
  tf$image$resize( size = shape(SIZE,SIZE)) %>% k_expand_dims(axis=1)
}
      
  shape<-dataset %>% subset(image_file == paste0(ffnames[k],".tiff" )) %>% dplyr::select(width_pixels, height_pixels) %>% unlist %>% as.vector
  nl<-c( seq(0,shape[1]-512, 512), shape[1]-512)
  nc<-c( seq(0,shape[2]-512, 512) , shape[2]-512)
  nn<-expand.grid(nl,nc)
  # walk2(nn[,1],nn[,2],makePng,im=im,mask=mask)
  wz=100
  sl<-c( seq(0,shape[1]-512 -wz, 512) + wz, shape[1]-512)
  sc<-c( seq(0,shape[2]-512 -wz, 512) + wz, shape[2]-512)
  ss<-expand.grid(sl,sc)
  
  wz=400
  ql<-c( seq(0,shape[1]-512 -wz, 512) + wz, shape[1]-512)
  qc<-c( seq(0,shape[2]-512 -wz, 512) + wz, shape[2]-512)
  qq<-expand.grid(ql,qc)
  
#predsub<-matrix(0, nrow= shape[1],ncol=shape[2])

pb <- txtProgressBar(min = 0, max = nrow(nn), style = 3)

which(nn$Var1 ==23040 & nn$Var2 == 17920)
i= 2741
idxt<- vector(mode="integer")
for(i in seq_len(nrow(nn)) ){
  img<- makeimg(nn[i,1],nn[i,2],im=im)
  if( img %>% as.array %>% max< .2){next}
  pred<- predict(model, img) %>%  tf$image$resize( size = shape(512,512)) %>%
    k_squeeze(axis=1) %>% k_squeeze(axis=3) %>% as.array(dim=c(512,512))
 #else{
  pred<- pred %>% as.cimg > thr
  pred <- pred %>% shrink(50) %>% grow(50)  #%>%as.matrix
  idx<- which(pred ==1)
  idxt<-c(idx,idxt)
  
  
  # x<- img %>% .[1,,,]%>% tf$image$resize( size = shape(512,512)) %>% k_expand_dims(3) %>%   as.array()  %>% as.cimg   %>% plot
  # colorise(x,pred,"blue", alpha = 0.3) %>% plot
  # # predsub[  (nn[i,1]+1):(nn[i,1]+512),  (nn[i,2]+1):(nn[i,2]+512)] <- pred
  # a<- mask2rle(pred)
  # b<- rle2mask(a, shape = c(512,512)) #OK works check !
  
  setTxtProgressBar(pb, i)
  if(i %%100 ==0){gc()}
}

######
fx<- function(wz){
  slw<-c(0, seq(0,shape[1]-512 -wz, 512) + wz, shape[1]-512)
  scw<-c(0, seq(0,shape[2]-512 -wz, 512) + wz, shape[2]-512)
  # sl<-c( seq(0,shape[1]-512 , 512) , shape[1]-512)
  # sc<-c( seq(0,shape[2]-512 , 512) , shape[2]-512)
  ll<- c(slw)
  cc<-c(scw)
  ss<-expand.grid(ll,cc)

  for( i in 1:nrow(ss)){
  img<- makeimg(ss[i,1],ss[i,2],im=im)
  pred<- predict(model, img) %>%  tf$image$resize( size = shape(512,512)) %>%
  k_squeeze(axis=1) %>% k_squeeze(axis=3) %>% as.array(dim=c(512,512))

   ppred<-  predsub[  (ss[i,1]+1):(ss[i,1]+512),  (ss[i,2]+1):(ss[i,2]+512)]
   predsub[  (ss[i,1]+1):(ss[i,1]+512),  (ss[i,2]+1):(ss[i,2]+512)] <- (ppred + pred) 
  setTxtProgressBar(pb, i)
  if(i %%100 ==0){gc()}
  }
  return(predsub)
}
#####

# for(i in seq_len(nrow(ss)) ){
# 
#   img<- makeimg(ss[i,1],ss[i,2],im=im)
#   pred<- predict(model, img) %>%  tf$image$resize( size = shape(512,512)) %>%
#     k_squeeze(axis=1) %>% k_squeeze(axis=3) %>% as.array(dim=c(512,512))
#   if( img %>% as.array %>% max< .2){next}else{
#   #pred<- pred %>% as.cimg > thr
#   #pred <- pred %>% shrink(50) %>% grow(50)  %>%as.matrix
#   # img %>% .[1,,,] %>% k_expand_dims(3) %>% as.array() %>% as.cimg %>% plot()
#   #pred<- pred > thr
#   }
#    ppred<-  predsub[  (ss[i,1]+1):(ss[i,1]+512),  (ss[i,2]+1):(ss[i,2]+512)]
#    predsub[  (ss[i,1]+1):(ss[i,1]+512),  (ss[i,2]+1):(ss[i,2]+512)] <- (ppred + pred) 
# 
#   setTxtProgressBar(pb, i)
#   if(i %%100 ==0){gc()}
# }
# for(i in seq_len(nrow(qq)) ){
# 
#   img<- makeimg(qq[i,1],qq[i,2],im=im)
#   pred<- predict(model, img) %>%  tf$image$resize( size = shape(512,512)) %>%
#     k_squeeze(axis=1) %>% k_squeeze(axis=3) %>% as.array(dim=c(512,512))
#   if( img %>% as.array %>% max< .2){next}else{
#   #pred<- pred %>% as.cimg > thr
#   #pred <- pred %>% shrink(50) %>% grow(50)  %>%as.matrix
#   # img %>% .[1,,,] %>% k_expand_dims(3) %>% as.array() %>% as.cimg %>% plot()
#   #pred<- pred > thr
#   }
#    ppred<-  predsub[  (qq[i,1]+1):(qq[i,1]+512),  (qq[i,2]+1):(qq[i,2]+512)]
#    predsub[  (qq[i,1]+1):(qq[i,1]+512),  (qq[i,2]+1):(qq[i,2]+512)] <- (ppred + pred) 
# 
#   setTxtProgressBar(pb, i)
#   if(i %%100 ==0){gc()}
# }
# walk(1:nrow(nn),fx,wz=100)
# walk(1:nrow(nn),fx,wz=400)
# predsub<-fx(100)
# predsub<-fx(200)
# predsub<-fx(300)
# predsub<-fx(400)
windows<- seq(20,480,20)
for(i in windows){
  predsub<-fx(i)
}
predsub<- predsub /(length(windows) + 1)

xx<- predsub
predsub<-xx
for(i in seq_len(nrow(nn)) ){
  pred<- predsub[  (nn[i,1]+1):(nn[i,1]+512),  (nn[i,2]+1):(nn[i,2]+512)] 
  pred<- pred %>% as.cimg > 0.6
  pred <- pred %>% shrink(50) %>% grow(50)  %>%as.matrix 
  predsub[  (nn[i,1]+1):(nn[i,1]+512),  (nn[i,2]+1):(nn[i,2]+512)]  <- pred
  setTxtProgressBar(pb, i)
  if(i %%100 ==0){gc()}
}



x<- predsub %>% as.cimg
imager::save.image(x,file=file.path(EVAL,"pred8.png"))

b<- x %>% threshold() %>% as.cimg
imager::save.image(b,file=file.path(EVAL,"predb.png"))

bb<- b %>% shrink(50) %>% grow(50) %>% as.cimg
imager::save.image(bb,file=file.path(EVAL,"predbb.png"))

mtrue<- makeMask(k)
imager::save.image(mtrue,file= file.path(EVAL,"true.png" ) )

# imm<- im[[1]] %>% as.numeric %>% as.cimg



 
 # which threshould is better?
mtrue<- makeMask(6)
 ttrue<- mtrue %>% k_variable()
# for(i in seq_len(nrow(nn)) ){
fx<- function(tx){ 
    predsub<-xx
  for(i in 1:nrow(nn)){
  pred<- predsub[  (nn[i,1]+1):(nn[i,1]+512),  (nn[i,2]+1):(nn[i,2]+512)]
  pred<- pred %>% as.cimg > tx
  pred <- pred %>% shrink(50) %>% grow(50)  %>%as.matrix 
  predsub[  (nn[i,1]+1):(nn[i,1]+512),  (nn[i,2]+1):(nn[i,2]+512)]  <- pred
  setTxtProgressBar(pb, i)
  }
  tpred<- predsub %>% k_variable()
  res<- dice(ttrue,tpred) %>% as.array
 return(res)
}
seqs<- seq(.61,.63,.01)
res<- map(seqs,fx); names(res)<- seqs

```

```{r}
 # which threshould is better?
 ttrue<- mtrue %>% k_variable()
# for(i in seq_len(nrow(nn)) ){
fxs<- function(tx){ 
    predsub<-xx
  for(i in 1:nrow(nn)){
  pred<- predsub[  (nn[i,1]+1):(nn[i,1]+512),  (nn[i,2]+1):(nn[i,2]+512)] /5  #(length(windows) + 1)
  pred<- pred %>% as.cimg > tx
  pred <- pred %>% shrink(50) %>% grow(50)  %>%as.matrix 
  predsub[  (nn[i,1]+1):(nn[i,1]+512),  (nn[i,2]+1):(nn[i,2]+512)]  <- pred
  setTxtProgressBar(pb, i)
  }
  tpred<- predsub %>% k_variable()
  res<- dice(ttrue,tpred) %>% as.array
  gc()
 return(res)
}
# sh<- gr<-seq(20,70,10)
# sg<-expand.grid(sh,gr)
seqs<-seq(5.9,6.4,.1)
res<- map(seqs,fxs); names(res)<-seqs #paste0(sg[,1], "_",sg[,2])

```


```{r}
model<-load_model_hdf5(file.path(EVAL,"m500_50_12000.hdf5"), custom_objects = c("bce_dice_loss"= bce_dice_loss, "dice"=dice))

```


